PANCHANGE_data_preprocessing

### 2020-09-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
modified control definition for nbr

```{r mhd control EDGI NBR}
if(EDGI == TRUE | NBR == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    autism_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0" &
      mhd.prefer_not_to_answer_numeric == "0" & # added 31. August 2020
      mhd.prefer_not_to_answer.1_numeric == "0" & # added 31. August 2020
      mhd.dont_know_numeric == "0" & # added 31. August 2020
      mhd.dont_know.1_numeric == "0" & # added 31. August 2020
      mhd.other_please_tell_us_more_numeric == "0" &
      mhd.dont_know_eating_disorder_numeric == "0",# &
#      mhd.prefer_not_to_answer_eating_disorder_numeric == "0" &
#      mhd.other_eating_disorder_numeric == "0",
    true = 1,
    false = 0, 
    NA_real_)
  )

@@

mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above,
    mhd.other_please_tell_us_more
  )

#mhd.raw.id %>%
#  count(
#    control,
#    age_
#  )
}
```

>>>>

```{r mhd control EDGI NBR}
if(EDGI == TRUE | NBR == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    autism_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0" &
      mhd.prefer_not_to_answer_numeric == "0" & # added 31. August 2020
      mhd.prefer_not_to_answer.1_numeric == "0" & # added 31. August 2020
      mhd.dont_know_numeric == "0" & # added 31. August 2020
      mhd.dont_know.1_numeric == "0" & # added 31. August 2020
      mhd.other_please_tell_us_more_numeric == "0" &
      mhd.dont_know_eating_disorder_numeric == "0" &
      mhd.prefer_not_to_answer_eating_disorder_numeric == "0" &
      mhd.other_eating_disorder_numeric == "0",
    true = 1,
    false = 0, 
    NA_real_)
  )

@@

mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above,
    mhd.other_please_tell_us_more
  )
}
```

```{r mhd check none of the above}
if(NBR == TRUE) {
mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above,
    mhd.other_please_tell_us_more,
    mhd.other_eating_disorder
  )
}
```
